---
title: "Analysis"
output:
  html_document:
    toc: true
    number_sections: true
---

- Report generated `r date()`

```{r echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}

source(file.path("..", "_setup.R"))
opts_chunk$set(warning = FALSE, error = FALSE, message = FALSE, echo = FALSE)
num.levels <- 4 # Number of levels for interaction plots
modify.vals <- list() # Modify variable levels defauls
modify.vals[["Power.distance"]] <- c(1,2,3,4,5,6)
modify.vals[["Resistance.to.change"]] <- c(2,3,4,5,6)
modify.vals[["Core.self.evaluation"]] <- c(3,4,5,6)
modify.vals[["Openness.to.change"]] <- c(4,5,6,7,8,9)

fig.width1 <- 4; fig.height1 <- 4
fig.width2 <- 8; fig.height2 <- 6

data <- dget(file.path(gv$data, 'data2.dput'))
labels <- attr(data, "labels")
var.key <- c("Power.distance", "Power.distance.cen", "Collectivist", "Collectivist.cen","Resistance.to.change", "Resistance.to.change.cen", "Core.self.evaluation", "Core.self.evaluation.cen" ) #, "Openness.to.change")
var.dem <- c("Age", "Gender", "Education",  "Manager")

data <- transform(data, Power.distance.cen = Power.distance - mean(Power.distance, na.rm = TRUE))
data <- transform(data, Collectivist.cen = Collectivist -mean(Collectivist, na.rm = TRUE))
data <- transform(data, Resistance.to.change.cen = Resistance.to.change -mean(Resistance.to.change, na.rm = TRUE))
data <- transform(data, Core.self.evaluation.cen = Core.self.evaluation -mean(Core.self.evaluation, na.rm = TRUE))

labels <- c(labels, 
           Power.distance.cen = as.character(labels["Power.distance"]),
           Collectivist.cen = as.character(labels["Collectivist"]),
              Resistance.to.change.cen = as.character(labels["Resistance.to.change"]),
              Core.self.evaluation.cen = as.character(labels["Core.self.evaluation"])
 )           
            
data.comp <- dget(file.path(gv$data, 'data.comp.dput'))

```

# Correlations of Constructive Voice Behavior, Power distance, Collectivist, Resistance to change, Core self evaluation. Inc mean and SD. 

It does not make sense to have correlations with demographics as these are factors

```{r corr_table, results = "asis"}
digits <- 2

corr.data <- subset(data, select = c("Constructive.voice.behaviour",
                                     "Power.distance",
                                     "Collectivist", 
                                     "Resistance.to.change",
                                     "Core.self.evaluation" 
                                    ))
corr.data.long <- melt(corr.data, id.var = NULL)

corr <- ddply(corr.data.long, .(variable), function(x){
  ddply(corr.data.long, .(variable), function(y, z=x){
  
    test <- cor.test(z$value, y$value)
   data.frame(
     variable1 = unique(z$variable),
    variable2 = unique(y$variable),
    corr = format(test$estimate, digits = digits),
    CI = paste0('(',  format(test$conf.int[1], digits = digits), ', ', 
                format(test$conf.int[2], digits = digits), ')'),
        p.value = format(test$p.value, digits = digits) 
    )
})
})

corr$variable <- NULL

corr <- melt(corr, id.vars = c("variable1", "variable2"), variable.name = "param")

corr <- dcast(corr, variable1 + param ~ variable2)

mean <- ddply(corr.data.long, .(variable), function(x){
  data.frame(mean = format(mean(x$value), digits = digits),
             SD = format(sqrt(var(x$value)), digits = digits)
             )
})

corr <-  merge(mean, corr, by.x = "variable", by.y = "variable1")

print(xtable(corr, align = c("l", "l", "r", "r", "l", rep("r", ncol(corr)-4))),
      type = "html",
      include.rownames = FALSE
)
```

# Cronbach alpha for Constructive Voice Behavior, Power distance, Collectivist, Resistance to change, Core self evaluation.

Using http://personality-project.org/r/html/alpha.html

## Constructive Voice Behavior

```{r alpha CVB}
alpha(data.comp[["CVB"]])
```

## Power distance

```{r alpha POW}
alpha(data.comp[["POW"]])
```

## Resistance to change

```{r alpha RTC}
alpha(data.comp[["RTC"]])
```

## Collectivist

```{r alpha COL}
alpha(data.comp[["COL"]])
```

## Core self evaluation

```{r alpha CSE}
alpha(data.comp[["CSE"]])
```

# Linear models for Constructive Voice Behavior

Assess the following dependent variables for Constructive Voice Behaviour, with and without adjustment for potential confounding with demographic varaibles.

1. Power distance 
2. Collectivist
3. Resistance to change 
4. Core Self Evaluation 

## Unadjusted regression

### Key variables

```{r key unadjusted regression, results = "asis"}
mod <- list()
for(i in 1:length(var.key)){
  formula <- as.formula(paste("Constructive.voice.behaviour ~ ", var.key[i]))
  mod[[var.key[i]]] <- lm(formula, data = data)
  
  #kable(summary(mod[[var.key[i]]]))
  
  print(xtable(summary(mod[[var.key[i]]])),
      type = "html")
  
  cat("<br>")
  
}

```

```{r, fig.width = fig.width1, fig.height = fig.height1}
for(i in 1:length(mod)){
print(ggplotRegression(mod[[i]]))
}
```

### Demographic variables

```{r demographics unadjusted regression, results = "asis"}
mod <- formula <- list()
for(i in 1:length(var.dem)){
  formula[[var.dem[i]]] <- as.formula(paste("Constructive.voice.behaviour ~ ", var.dem[i]))
  mod[[var.dem[i]]] <- lm(formula[[var.dem[i]]], data = data)
  
  print(xtable(summary(mod[[var.dem[i]]])),
      type = "html")
  
  cat("<br>")
}

```

```{r, fig.width = fig.width1, fig.height = fig.height1}
for(i in 1:length(mod)){
  line.data <- data.frame(x = 1:length(unlist(mod[[i]]$xlevels)), 
                          y = mod[[i]]$coeff + mod[[i]]$coeff[1])
  line.data$y[1] <- line.data$y[1] - mod[[i]]$coeff[1]
  names(line.data) <- c(names(mod[[i]]$model)[2], "Constructive.voice.behaviour")
  
   p <- ggplot(mod[[i]]$model, aes_string(x = names(mod[[i]]$model)[2], y = names(mod[[i]]$model)[1])) + 
    geom_point(position = position_jitter(w = 0.05, h = 0)) +
     geom_path(data = line.data, col = "red", size = 1) +
    xlab(labels[names(mod[[i]]$model)[2]]) + ylab(labels[names(mod[[i]]$model)[1]]) +
     theme(axis.text.x = element_text(angle = 30, hjust = 1))
 
print(p)
}
```


## Adjustment for demographic varaibles
### Key variables with main effects for demographic varaibles

This adjusts for possible confounding by the demographic variables.

```{r key adjusted regression with main effects, results = "asis"}
mod <- list()

for(i in 1:length(var.key)){
  formula <- as.formula(paste("Constructive.voice.behaviour ~ ", var.key[i], 
                              "+", paste(var.dem, collapse = " + ")
                              ))
  
  mod[[var.key[i]]] <- lm(formula, data = data)
   print(xtable(summary(mod[[var.key[i]]])),
      type = "html")
 
  cat("<br>")
}

```

```{r, fig.width = fig.width1, fig.height = fig.height1}
for(i in 1:length(mod)){
print(ggplotRegression(mod[[i]]))
}
```

## Multivariate regression

### Key variables multivariate regression

```{r key multivariate regression, results = "asis"}
cen <- grep(".cen", var.key, value = TRUE)
not.cen <- var.key[-match(cen, var.key)]

  formula <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                              paste(not.cen, collapse = " + ")))
  mod <- lm(formula, data = data)
  
  print(xtable(summary(mod)),
      type = "html")
  
  cat("<br>")

  formula <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                              paste(cen, collapse = " + ")))
  mod <- lm(formula, data = data)
  
  print(xtable(summary(mod)),
      type = "html")
  
  cat("<br>")

```

### Demographics multivaraite regression
```{r demo multivariate regression, results = "asis"}

  formula <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                              paste(var.dem, collapse = " + ")))
  mod <- lm(formula, data = data)
  
  print(xtable(summary(mod)),
      type = "html")
  
  cat("<br>")

```

# Modifiers for the effect of key variables on Constructive Voice Behavior

Assess the following modifers for the effect of key variables on Constructive Voice Behaviour, with and without adjustment for potential confounding with demographic varaibles.
Continuous variables have all been centered.

1. Resistance to change moderates the effect of power distance on constructive voice behaviour

2. Core Self Evaluation moderates the effect of power distance on constructive voice behaviour  

3. Collectivist moderates the effect of power distance on constructive voice behaviour  

4. Core Self Evaluation moderates the effect of resistance to change on constructive voice behaviour 

5. Collectivist moderates the effect of resistance to change on constructive voice behaviour 

6. Collectivist moderates the effect of Core Self Evaluation on constructive voice behaviour 

```{r}
mod <- mod.adj <- formula <- modify <- titles <- list()
digits <- 1

formula[[1]] <- "Constructive.voice.behaviour ~ Power.distance.cen*Resistance.to.change.cen"
modify[[1]] <- round(modify.vals[["Resistance.to.change"]]- mean(data$Resistance.to.change, na.rm = TRUE), digits)
titles[[1]] <- "Resistance to change moderates the effect of power distance on constructive voice behaviour"

formula[[2]] <- "Constructive.voice.behaviour ~ Power.distance.cen*Core.self.evaluation.cen"
modify[[2]] <- round(modify.vals[["Core.self.evaluation"]] - mean(data$Core.self.evaluation, na.rm = TRUE), digits)
titles[[2]] <- "Core Self Evaluation moderates the effect of power distance on constructive voice behaviour"  

formula[[3]] <- "Constructive.voice.behaviour ~ Power.distance.cen*Collectivist.cen"
modify[[3]] <- round(modify.vals[["Collectivist"]] - mean(data$Collectivist, na.rm = TRUE), digits)
titles[[3]] <- "Collectivist moderates the effect of power distance on constructive voice behaviour"  

formula[[4]] <- "Constructive.voice.behaviour ~ Resistance.to.change.cen*Core.self.evaluation.cen"
modify[[4]] <- round(modify.vals[["Core.self.evaluation"]] - mean(data$Core.self.evaluation, na.rm = TRUE), digits)
titles[[4]] <- "Core Self Evaluation moderates the effect of resistance to change on constructive voice behaviour" 

formula[[5]] <- "Constructive.voice.behaviour ~ Resistance.to.change.cen*Collectivist.cen"
modify[[5]] <- round(modify.vals[["Collectivist"]] - mean(data$Collectivist, na.rm = TRUE), digits)
titles[[5]] <- "Collectivist moderates the effect of resistance to change on constructive voice behaviour" 

formula[[6]] <- "Constructive.voice.behaviour ~ Core.self.evaluation.cen*Collectivist.cen"
modify[[6]] <- round(modify.vals[["Collectivist"]] - mean(data$Collectivist, na.rm = TRUE), digits)
titles[[6]] <- "Collectivist moderates the effect of Core Self Evaluation on constructive voice behaviour" 

formula.adj <- lapply(formula, function(x){paste(x, "+", paste(var.dem, collapse = " + "))})

```



```{r modifier unadjusted regression, results = "asis", fig.width = fig.width2, fig.height = fig.height2}

make.modify.vals <- function(x, digits = 2){
mean <- mean(x)
sd <- sqrt(var(x))
out <- round(c(mean + sd, mean - sd), digits = digits)
return(out)
}

for(i in 1:length(formula)){
  
  cat("<h2>", titles[[i]], "</h2>")
  
cat("<h3> Unadjusted </h3>")
mod[[i]] <- lm(as.formula(formula[[i]]), data = data)
print(xtable(summary(mod[[i]])), type = "html")
cat("R^2 = ", summary(mod[[i]])$r.squared, "\n", sep = "")
cat("<br>")
#print(ggplotCtsInteraction(mod[[i]], modify.vals = modify[[i]], alpha = 0))

print(ggplotCtsInteraction(mod[[i]], 
                           v.line = make.modify.vals(mod[[i]]$model[,2]),
                           modify.vals = make.modify.vals(mod[[i]]$model[,3]), alpha = 0, SDplot = TRUE))

sd.vals <- make.modify.vals(mod[[i]]$model[,3])
upp.sd <- c(SD = "+1 SD", unlist(find.slope(mod[[i]], var = names(mod[[i]]$model)[2], inter.val = sd.vals[1])))
low.sd <- c(SD = "-1 SD", unlist(find.slope(mod[[i]], var = names(mod[[i]]$model)[2], inter.val = sd.vals[2])))

  print(xtable(rbind(upp.sd, low.sd)), type = "html")

####

cat("<h3> Adjusted for demographic variables, plotted at reference level </h3>")
mod.adj[[i]] <- lm(as.formula(formula.adj[[i]]), data = data)
print(xtable(summary(mod.adj[[i]])), type = "html")
cat("R^2 = ", summary(mod.adj[[i]])$r.squared, "\n", sep = "")
cat("<br>")
print(ggplotCtsInteraction(mod.adj[[i]], 
                           v.line = make.modify.vals(mod.adj[[i]]$model[,2]),
                           modify.vals = make.modify.vals(mod.adj[[i]]$model[,3]), alpha = 0, SDplot = TRUE))
cat("<br>")

# regression coef and slope for each SD line
sd.vals <- make.modify.vals(mod.adj[[i]]$model[,3])
upp.sd <- c(SD = "+1 SD", unlist(find.slope(mod.adj[[i]], var = names(mod.adj[[i]]$model)[2], inter.val = sd.vals[1])))
low.sd <- c(SD = "-1 SD", unlist(find.slope(mod.adj[[i]], var = names(mod.adj[[i]]$model)[2], inter.val = sd.vals[2])))

  print(xtable(rbind(upp.sd, low.sd)), type = "html")
}
```


## Look for interactions with demographic variables

```{r, results = "asis"}
mod <- step.mod <- list()
for(i in 1:length(var.key)){
  formula <- as.formula(paste("Constructive.voice.behaviour ~ ", var.key[i],  "*(", paste(var.dem, collapse = " + "), ")"))
  
  cat("<h3>", labels[var.key[i]], "</h3>")
  
  mod[[var.key[i]]] <- lm(formula, data = data) 
   step.mod[[var.key[i]]] <- step(mod[[var.key[i]]], trace = 0)
  
  cat(paste0(labels[var.key[i]], ": Initial model\n"))
  print(xtable(summary(mod[[var.key[i]]])), type = "html")
   # print(kable(summary(mod[[var.key[i]]])$coeff))

  
  cat(paste0(labels[var.key[i]], ": Final AIC model\n"))
  print(xtable(summary(step.mod[[var.key[i]]])), type = "html")
  #print(kable(summary(step.mod[[var.key[i]]])$coeff))
  #print(xtable(anova(step.mod[[var.key[i]]])), type = "html")
 
  cat("<br>")
  
}

```

# Core self evaluation as a modrator for the effect of resistance to change on constructive voice behaviour

Fit three models

* Demographics only
* Demographics with resistance to change and core self evaluation as main effects
* Demographics with resistance to change and core self evaluation as main and interaction effects

```{r, results = "asis", fig.width = fig.width2, fig.height = fig.height2}
mod3.d <- mod3.dm <- mod3.dmi <-list()

 formula.d <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                               paste(var.dem, collapse = " + "))
                         )

 formula.dm <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                                "Resistance.to.change.cen + Core.self.evaluation.cen + ",
                                paste(var.dem, collapse = " + ")                          
                                )
                         )

 formula.dmi <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                                  "Resistance.to.change.cen * Core.self.evaluation.cen + ",
                                paste(var.dem, collapse = " + ")                         
                                )
                         )

mod3.d <-  lm(formula.d, data = data)  
  cat(paste0("Demographics only\n"))
  print(xtable(summary(mod3.d)), type = "html")
cat("R^2 = ", summary(mod3.d)$r.squared, "\n", sep = "")
cat("adj R^2 = ", summary(mod3.d)$adj.r.squared, "\n", sep = "")
cat("<br>")

mod3.dm <-  lm(formula.dm, data = data)  
  cat(paste0("Demographics with resistance to change and core self evaluation as main effects\n"))
  print(xtable(summary(mod3.dm)), type = "html")
cat("R^2 = ", summary(mod3.dm)$r.squared, "\n", sep = "")
cat("adj R^2 = ", summary(mod3.dm)$adj.r.squared, "\n", sep = "")
cat("<br>")

mod3.dmi <-  lm(formula.dmi, data = data)  
  cat(paste0("Demographics with resistance to change and core self evaluation as main and interaction effects\n"))
  print(xtable(summary(mod3.dmi)), type = "html")

cat("R^2 = ", summary(mod3.dmi)$r.squared, "\n", sep = "")
cat("adj R^2 = ", summary(mod3.dmi)$adj.r.squared, "\n", sep = "")
cat("<br>")

print(ggplotCtsInteraction(mod3.dmi, 
                           v.line = make.modify.vals(mod3.dmi$model[,2]), 
                           modify.vals = make.modify.vals(mod3.dmi$model[,3]), 
                           alpha = 0, SDplot = TRUE))

# regression coef and slope for each SD line
sd.vals <- make.modify.vals(mod3.dmi$model[,3])
upp.sd <- c(SD = "+1 SD", unlist(find.slope(mod3.dmi, var = "Resistance.to.change.cen", inter.val = sd.vals[1])))
low.sd <- c(SD = "-1 SD", unlist(find.slope(mod3.dmi, var = "Resistance.to.change.cen", inter.val = sd.vals[2])))

  print(xtable(rbind(upp.sd, low.sd)), type = "html")
```

# Resistance to change as a modrator for the effect of core self evaluation on constructive voice behaviour

Fit three models

* Demographics only
* Demographics with resistance to change and core self evaluation as main effects
* Demographics with resistance to change and core self evaluation as main and interaction effects

```{r, results = "asis", fig.width = fig.width2, fig.height = fig.height2}
mod3.d <- mod3.dm <- mod3.dmi <-list()

 formula.d <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                               paste(var.dem, collapse = " + "))
                         )

 formula.dm <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                                "Core.self.evaluation.cen + Resistance.to.change.cen +  ",
                                paste(var.dem, collapse = " + ")                          
                                )
                         )

 formula.dmi <- as.formula(paste("Constructive.voice.behaviour ~ ", 
                                  "Core.self.evaluation.cen*Resistance.to.change.cen + ",
                                paste(var.dem, collapse = " + ")                         
                                )
                         )

mod3.d <-  lm(formula.d, data = data)  
  cat(paste0("Demographics only\n"))
  print(xtable(summary(mod3.d)), type = "html")
cat("R^2 = ", summary(mod3.d)$r.squared, "\n", sep = "")
cat("adj R^2 = ", summary(mod3.d)$adj.r.squared, "\n", sep = "")
cat("<br>")

mod3.dm <-  lm(formula.dm, data = data)  
  cat(paste0("Demographics with resistance to change and core self evaluation as main effects\n"))
  print(xtable(summary(mod3.dm)), type = "html")
cat("R^2 = ", summary(mod3.dm)$r.squared, "\n", sep = "")
cat("adj R^2 = ", summary(mod3.dm)$adj.r.squared, "\n", sep = "")
cat("<br>")

mod3.dmi <-  lm(formula.dmi, data = data)  
  cat(paste0("Demographics with resistance to change and core self evaluation as main and interaction effects\n"))
  print(xtable(summary(mod3.dmi)), type = "html")

cat("R^2 = ", summary(mod3.dmi)$r.squared, "\n", sep = "")
cat("adj R^2 = ", summary(mod3.dmi)$adj.r.squared, "\n", sep = "")
cat("<br>")

print(ggplotCtsInteraction(mod3.dmi, 
                           v.line = make.modify.vals(mod3.dmi$model[,2]), 
                           modify.vals = make.modify.vals(mod3.dmi$model[,3]), 
                           alpha = 0, SDplot = TRUE))

# regression coef and slope for each SD line

sd.vals <- make.modify.vals(mod3.dmi$model[,3])
upp.sd <- c(SD = "+1 SD", unlist(find.slope(mod3.dmi, var = "Core.self.evaluation.cen", inter.val = sd.vals[1])))
low.sd <- c(SD = "-1 SD", unlist(find.slope(mod3.dmi, var = "Core.self.evaluation.cen", inter.val = sd.vals[2])))

  print(xtable(rbind(upp.sd, low.sd)), type = "html")
```

***

Session Information  
```{r, echo = FALSE}
sessionInfo()
```
