---
title: "Mediation"
output:
  html_document:
    toc: true
    number_sections: true
---

- Report generated `r date()`

```{r echo = FALSE}
source(file.path("..", "_setup.R"))
opts_chunk$set(warning = FALSE, error = FALSE, message = FALSE, echo = FALSE)
fig.width1 <- 4
fig.height1 <- 4

data <- dget(file.path(gv$data, 'data.dput'))
labels <- attr(data, "labels")
var.ivt <- c("Don.t.bypass.boss.upward", "Presumed.Target.Identification", "Don.t.embarass.boss.publicly", "Negative.career.consequences.of.voice")
var.key <- c("Power.Distance", "Resistance.to.change", "Openess.to.change")
var.dem <- c("Age", "Gender", "Level.of.education",                      
                      "Manager", "Duration.current.organisation")
var.cou <- c("Num.countries.12.months",
             "Countries.Asia", "Countries.Europe.Australia" , "Countries.Latin.America",  "Countries.North.America", "Countries.Africa")
```

# Assess mediators of Constructive Voice Behavior

## Assess IVT variables as mediators for effect of key variables on Constructive Voice Behavior

Need to pass three tests:

1. Test "independent" is significant in model 1: dependent ~ independent (+ covar)
2. Test "independent" is significant in model 2:  mediator ~ independent (+ covar)
3. Test "mediator" is significant in model 3:  dependent ~ independent + mediator (+ covar)

In addition, if all three tests are passed,  can test of complete or partial mediation by test "independent" is significant in model 3:  dependent ~ independent + mediator (+ covar).


```{r IVT as mediators, results = "asis"}
for(independent in var.key){
  for(mediator in var.ivt){
    
     cat(paste0("<br>Testing IVT variable: <b>", labels[mediator], 
                "</b><br>as a mediator for effect of<br><b>",
                labels[independent], "</b> on Constructive Voice Behavior<br>"))
 
    results <- test.med(
  dependent = "Constructive.Voice.Behavior",
  independent = independent,
  mediator = mediator,
  covar = NULL, #var.dem, # Other covariates to include in the model
  data = data
)

print.test.med(results)
  }
}

```

## Assess key variables as mediators for effect of IVT variables on Constructive Voice Behavior

```{r key as mediators, results = "asis"}
for(independent in var.ivt){
  for(mediator in var.key){
    
     cat(paste0("<br>Testing key variable: <b>", labels[mediator], 
                "</b><br>as a mediator for effect of<br><b>",
                labels[independent], "</b> on Constructive Voice Behavior<br>"))
 
    results <- test.med(
  dependent = "Constructive.Voice.Behavior",
  independent = independent,
  mediator = mediator,
  covar = NULL, #var.dem, # Other covariates to include in the model
  data = data
)

print.test.med(results)
  }
}

```