---
title: "Exploratory plots"
output:
  html_document:
    toc: true
    number_sections: true
---

- Report generated `r date()`

```{r echo = FALSE}
source(file.path("..", "_setup.R"))
opts_chunk$set(warning = FALSE, error = FALSE, message = FALSE, echo = FALSE)

data <- dget(file.path(gv$data, 'data.dput'))
labels <- attr(data, "labels")
var.ivt <- names(data)[2:5]
var.key <- c("Power.Distance", "Resistance.to.change", "Openess.to.change")
var.dem <- c("Age", "Gender", "Level.of.education",                      
                      "Manager", "Duration.current.organisation")
var.cou <- c("Num.countries.12.months",
             "Countries.Asia", "Countries.Europe.Australia" , "Countries.Latin.America",  "Countries.North.America", "Countries.Africa")
```

# Relationship with IVT variables with other variables

```{r}
# Which variables are independent, dependent and effect modifiers
var.indep <- names(data)[2:5]
var.dep <- names(data)[6:11]
var.mod <- names(data)[12:23]

# Makea long dataset, with indep and dep variables values as colums
long.indep <- melt(data, id.vars = "ResponseID", measure.vars = var.indep, variable.name = "var.indep", value.name = "value.indep")
long.dep <- melt(data, id.vars = "ResponseID", measure.vars = var.dep, variable.name = "var.dep", value.name = "value.dep")

long <- merge(long.indep, long.dep, by = "ResponseID")
long <- merge(long, data[, c("ResponseID", var.mod)], by = "ResponseID")

long$var.indep <- labels[as.character(long$var.indep)]
long$var.dep <- labels[as.character(long$var.dep)]

long$var.indep <- factor(long$var.indep, levels = labels[var.indep])
long$var.dep <- factor(long$var.dep, levels = labels[var.dep])

```

## Plot of the IVT variables against other variables
```{r, fig.width = 10, fig.height = 10}
p <- ggplot(long, aes(x = value.indep, y = value.dep)) +
  facet_grid(var.dep ~ var.indep, scale = "free") +
  geom_point() +
  geom_smooth() +
  xlab("Score") + ylab("Score")

print(p)
```

## Correlation of IVT with other variables
```{r corr_table, results = "asis"}
digits <- 2

corr <- ddply(long, .(var.indep, var.dep), function(x){
  test <- cor.test(x$value.indep, x$value.dep)
  data.frame(
    corr = test$estimate,
    p.value = test$p.value,
    low = test$conf.int[1],
    upp = test$conf.int[2]
    )
})

corr <- melt(corr, measure.vars = c("corr", "p.value", "low", "upp"))
corr$value <- format(corr$value, digits = digits)

corr.CI <- ddply(corr, .(var.indep, var.dep), function(x){
  data.frame(variable = "CI",
             value = paste0('(', subset(x, variable == "low")$value, ', ', subset(x, variable == "upp")$value, ')'))
})

corr <- rbind(subset(corr, variable %in% c("corr", "p.value")), corr.CI)
corr <- dcast(corr, var.indep + variable ~ var.dep)

print(xtable(corr, align = c("l", "l", rep("r", ncol(corr)-1))),
      type = "html",
      include.rownames = FALSE
)

```

# Relationship of variables with Constructive Voice Behavior
## Plots of Constructive Voice Behavior
### Hisogram of Constructive Voice Behavior

```{r}
ggplot(data, aes(x = Constructive.Voice.Behavior)) +
  geom_histogram() +
  xlab(labels["Constructive.Voice.Behavior"])
```

### Density of Constructive Voice Behavior

```{r}
ggplot(data, aes(x = Constructive.Voice.Behavior)) +
  geom_density() +
  xlab(labels["Constructive.Voice.Behavior"])
```

## Plots of IVT and Constructive Voice Behavior

```{r IVT vs Constructive.Voice.Behavior, fig.width = 5, fig.height = 8}
long.ivt <- melt(data, 
                   id.vars = c("ResponseID", "Constructive.Voice.Behavior"), 
                   measure.vars = var.ivt, 
                   variable.name = "var.ivt", value.name = "IVT")

long.ivt$var.ivt <- labels[as.character(long.ivt$var.ivt)]
long.ivt$var.ivt <- factor(long.ivt$var.ivt, levels = labels[var.ivt])

ggplot(long.ivt, aes(x = IVT, y = Constructive.Voice.Behavior)) +
  facet_wrap(~ var.ivt, ncol = 1) +
  geom_point() +
   geom_smooth() +
ylab(labels["Constructive.Voice.Behavior"]) + xlab("")
```

## Plots of key variables and Constructive Voice Behavior

```{r key vs Constructive.Voice.Behavior, fig.width = 6, fig.height = 6}
long.key <- melt(data, 
                   id.vars = c("ResponseID", "Constructive.Voice.Behavior"), 
                   measure.vars = var.key, 
                   variable.name = "var.key", value.name = "key")

long.key$var.key <- labels[as.character(long.key$var.key)]
long.key$var.key <- factor(long.key$var.key, levels = labels[var.key])

ggplot(long.key, aes(x = key, y = Constructive.Voice.Behavior)) +
  facet_wrap(~ var.key, ncol = 1) +
  geom_point() +
   geom_smooth() +
ylab(labels["Constructive.Voice.Behavior"]) + xlab("")
```

## Plots of demographic variables and Constructive Voice Behavior

```{r Demo vs Constructive.Voice.Behavior, fig.width = 6, fig.height = 8}
long.dem <- melt(data, 
                   id.vars = c("ResponseID", "Constructive.Voice.Behavior"), 
                   measure.vars = var.dem, 
                   variable.name = "var.dem", value.name = "dem")

long.dem$var.dem <- labels[as.character(long.dem$var.dem)]
long.dem$var.dem <- factor(long.dem$var.dem, levels = labels[var.dem])

ggplot(long.dem, aes(x = as.factor(dem), y = Constructive.Voice.Behavior)) +
  facet_wrap(~ var.dem, ncol = 1) +
  geom_violin() + 
    geom_point(position = position_jitter(w = 0.2, h = 0)) +
ylab(labels["Constructive.Voice.Behavior"]) + xlab("")

```

## Violin plots of country variables and Constructive Voice Behavior

```{r Num country vs Constructive.Voice.Behavior, fig.width = 6, fig.height = 4}
ggplot(data, aes(x = as.factor(Num.countries.12.months), y = Constructive.Voice.Behavior)) +
  geom_violin() + 
  geom_point(position = position_jitter(w = 0.2, h = 0)) +
ylab(labels["Constructive.Voice.Behavior"]) + xlab(labels["Num.countries.12.months"])
```

```{r Counties vs Constructive.Voice.Behavior, fig.width = 6, fig.height = 8}
var.cou0 <- var.cou[-1]
long.cou <- melt(data, 
                   id.vars = c("ResponseID", "Constructive.Voice.Behavior"), 
                   measure.vars = var.cou0, 
                   variable.name = "var.cou", value.name = "cou")

long.cou$var.cou <- labels[as.character(long.cou$var.cou)]
long.cou$var.cou <- factor(long.cou$var.cou, levels = labels[var.cou])

ggplot(long.cou, aes(x = as.factor(cou), y = Constructive.Voice.Behavior)) +
  facet_wrap(~ var.cou, ncol = 1) +
  geom_violin() + 
  geom_point(position = position_jitter(w = 0.2, h = 0)) +
ylab(labels["Constructive.Voice.Behavior"]) + xlab("")

```
