---
title: "Exploratory plots"
output:
  html_document:
    toc: true
    number_sections: true
---

- Report generated `r date()`

```{r echo = FALSE, warning = FALSE}
source(file.path("..", "_setup.R"))
opts_chunk$set(warning = FALSE, error = FALSE, message = FALSE, echo = FALSE)

data <- dget(file.path(gv$data, 'data2.dput'))
labels <- attr(data, "labels")
var.key <- c("Power.distance", "Resistance.to.change", "Core.self.evaluation", "Openness.to.change")
var.dem <- c("Age", "Gender", "Education",  "Manager")
```


# Correlation of Constructive Voice Behaviour with other variables
```{r corr_table, results = "asis"}
digits <- 2

long <-  melt(subset(data, select = c("ResponseID", "Constructive.voice.behaviour", var.key)),  id.vars = "ResponseID", variable.name = "var")

corr <- ddply(long, .(var), function(x){
  test <- cor.test(data$Constructive.voice.behaviour, x$value)
  data.frame(
    corr = test$estimate,
    p.value = test$p.value,
    low = test$conf.int[1],
    upp = test$conf.int[2]
    )
})

corr <- melt(subset(corr, subset = var != "Constructive.voice.behaviour"), 
             measure.vars = c("corr", "p.value", "low", "upp"))

corr$value <- formatC(corr$value, digits = digits, format = "g")
corr.CI <- ddply(corr, .(var), function(x){
  data.frame(variable = "CI",
             value = paste0('(', subset(x, variable == "low")$value, ', ', subset(x, variable == "upp")$value, ')'))
})

corr <- rbind(subset(corr, variable %in% c("corr", "p.value")), corr.CI)
corr <- dcast(corr, var ~ variable)

kable(corr, align = c("l","r", "r", "r"))

```

# Relationship of variables with Constructive Voice Behaviour
## Plots of Constructive Voice Behaviour
### Hisogram of Constructive Voice Behaviour

```{r}
ggplot(data, aes(x = Constructive.voice.behaviour)) +
  geom_histogram() +
  xlab(labels["Constructive.voice.behaviour"])
```

### Density of Constructive Voice Behaviour

```{r}
ggplot(data, aes(x = Constructive.voice.behaviour)) +
  geom_density() +
  xlab(labels["Constructive.voice.behaviour"])
```


## Plots of key variables and Constructive Voice Behaviour

```{r key vs Constructive.voice.behaviour, fig.width = 6, fig.height = 12}
long.key <- melt(data, 
                   id.vars = c("ResponseID", "Constructive.voice.behaviour"), 
                   measure.vars = var.key, 
                   variable.name = "var.key", value.name = "key")

long.key$var.key <- labels[as.character(long.key$var.key)]
long.key$var.key <- factor(long.key$var.key, levels = labels[var.key])

ggplot(long.key, aes(x = key, y = Constructive.voice.behaviour)) +
  facet_wrap(~ var.key, ncol = 1) +
  geom_point() +
   geom_smooth() +
ylab(labels["Constructive.voice.behaviour"]) + xlab("")
```

## Plots of demographic variables and Constructive Voice Behaviour

```{r Demo vs Constructive.voice.behaviour, fig.width = 6, fig.height = 4}
long.dem <- melt(data, 
                   id.vars = c("ResponseID", "Constructive.voice.behaviour"), 
                   measure.vars = var.dem, 
                   variable.name = "var.dem", value.name = "dem")

long.dem$var.dem <- labels[as.character(long.dem$var.dem)]
long.dem$var.dem <- factor(long.dem$var.dem, levels = labels[var.dem])

for(dem in var.dem){

p <- ggplot(data, aes_string(x = dem, y = "Constructive.voice.behaviour")) +
  geom_violin() + 
    geom_point(position = position_jitter(w = 0.2, h = 0)) +
ylab(labels["Constructive.voice.behaviour"]) + xlab(labels[dem]) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot(p)
}
```

## Plots of Resistance to change and Core self evaluation

```{r fig.width = 6, fig.height = 4}

p <- ggplot(data, aes(x = Resistance.to.change, y = Core.self.evaluation)) +
   geom_point() +
  geom_smooth() +
ylab(labels["Core.self.evaluation"]) + xlab(labels["Resistance.to.change"]) 
 
plot(p)

```

***

Session Information  
```{r, echo = FALSE}
sessionInfo()
```

